Measuring Political Freedom Around the World

### 2020-11-10 slides.Rmd
.

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, echo = FALSE)
library(gtsummary)
source(here::here("R", "visualization.R"))
options(digits = 3)
```

---
```{r echo=FALSE}
best_subsets %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(model, adj.r.squared) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 6))
```
---

@@

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

>>>>

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, echo = FALSE)
source(here::here("R", "regression.R"))
options(digits = 3)
```

---
```{r echo=FALSE}
subsets %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(model, adj.r.squared) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 6))
```
---

@@

# Introduction

# Model

# Findings

# Conclusions
